\thispagestyle{plain}
\addtocounter{page}{1}
\begin{center}
\Large
\textbf{\uppercase{Acknowledgements}}
\end{center}

The completion of this thesis project would not have been possible without the support of several individuals. First, I would like to thank my advisor Alan Ker. Despite my lack of economics background, Alan encouraged me to apply for the FARE program. His encouragement led to the completion of my masters, and enabled me to gain invaluable experience and skills. Alan's high academic standards and critical input elevated the quality and depth of this project. His renown as a researcher is well deserved. I would also like to thank my thesis committee member Bill Deen for his insight into the agronomic relationships underlying some of the questions addressed in this project, and the potential implications of our results. His knowledge in this area was crucial to the development of the empirical methods, and models used.

The academic culture in the FARE program has created an environment which is friendly and comfortable, as well as challenging for it's graduate students. This environment is maintained through the actions of everyone involved in the department. It has been a great place to learn, work, and make connections. In particular I would like to thank my fellow cohort of graduate students. The warmth and support provided has constantly exceeded expectation.

Finally, I would like to thank my family for your continual support and encouragement.  I attribute my academic curiosity in large part to my father, Jules, who started summarizing and explaining Scientific American articles to me when I was four.  To my mother, Janna, thank you for always being there for emotional support and for helping me to maintain perspective. You have both encouraged me to pursue my interests, and to always questions things. The environment you provided for me has made this easy to do, and your support is very much appreciated.